---
title: "HW2_Lian"
author: "Jiayi Lian"
date: "September 4, 2019"
output: pdf_document
---

# Homework2

## P3

It can help me know how far have you gone through in your project.I can also see what changes have been done after each version created. There is more convenience. If I am not satisfied with my final version, I am able to find proper immediate version to start. It would save my time to go back step by step.

## p4

Before munge, I took a glimpse of dats. I saw that colnames, rownames, obs are mixed together. I have to break the data into pieces then aggregate in a tidy format. Sometimes, obs are record in a string. So I should also split the string.

```{r include=FALSE}
install.packages('dplyr',repo="https://cran.cnr.Berkeley.edu/")
library('dplyr')
library('tidyr')
library('stats')
```

```{r}
# Store url 
# In the order of "sensory data, gold medal performance, brain weight vs body weight,
# triplicate measurements of tomato."
url_sensory<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/Sensory.dat"
url_gold<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/LongJumpData.dat"
url_brain<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/BrainandBodyWeight.dat"
url_tomato<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/tomato.dat"
#download into local memory
Sensory<-read.csv(url_sensory,header =  F,skip = 2,sep = "")
#manipulate data into a tidy format
#transfer data into a vector
dim_ori<-dim(Sensory)
Sen_2=c()
for (i in 1:dim_ori[1]) {
  if (sum(i == seq(1,dim_ori[1],3)))
  {Sen_2=c(Sen_2,as.matrix(Sensory[i,2:dim_ori[2]]))}
  else
  {Sen_2=c(Sen_2,as.matrix(Sensory[i,1:(dim_ori[2]-1)]))}
}
#transfer the vector into a data.frame
Sen_2<-data.frame(matrix(Sen_2,nrow = dim_ori[1],ncol = dim_ori[2]-1))
#change the name of data
colnames(Sen_2)<-paste('Operator',as.character(1:5))

text_paste<-c()
for (i in 1:10) {
  text_paste<-c(text_paste,seq(i+0.1,i+0.3,0.1))
}
rownames(Sen_2)<-paste('Item',as.character(text_paste))
#Show table of Sensory data
Sen_2
str(Sen_2)
summary(Sen_2)
```

```{r}
#load gold medal performance dat
gold<-read.csv(url_gold,header =  F,skip = 1,sep = "")
#mung
dim_gold<-dim(gold)
gold_2=c()
for (i in 1:dim_gold[1]) {
  if (sum(i == c(5,6)))
  {gold_2=c(gold_2,as.matrix(gold[i,1:(dim_gold[2]-2)]))}
  else
  {gold_2=c(gold_2,as.matrix(gold[i,1:dim_gold[2]]))}
}
gold_2<-data.frame(matrix(gold_2,ncol = 2,nrow = 22,byrow = T))
colnames(gold_2)<-c('Year','Long Jump')
rownames(gold_2)<-1:dim(gold_2)[1]
gold_2[1]<-gold_2[1]+1900
#show
gold_2
str(gold_2)
summary(gold_2)
```

```{r}
#load brain vs body weight dat
brain<-read.csv(url_brain,header = F,sep='',skip = 1)
#munge
dim_bra<-dim(brain)
braW_boW<-c()
for (i in 1:dim_bra[1]) {
  braW_boW<-c(braW_boW,as.matrix(brain[i,]))
}
not_na<-ifelse(is.na(braW_boW),F,T)
braW_boW<-braW_boW[not_na]
braW_boW<-data.frame(matrix(braW_boW,ncol=2,nrow = 62))
colnames(braW_boW)<-c('Body Weight','Brain Weight')
rownames(braW_boW)<-1:dim(braW_boW)[1]
#show
print(braW_boW)
str(braW_boW)
summary(braW_boW)
```
```{r}
#download tomato dat
tomato<-read.csv(url_tomato ,sep='',skip = 1,header = F)
#munge
t_colname<-as.matrix(paste('S_',as.character(seq(10000,30000,10000)),sep=""))
t_rowname<-as.matrix(tomato$V1[2:3])
t_meas<-c(as.matrix(tomato$V2[2]),as.matrix(tomato$V2[3]),as.matrix(tomato$V3[2]),as.matrix(tomato$V3[3]),as.matrix(tomato$V4[2]),as.matrix(tomato$V4[3]))
t_meas<-data.frame(matrix(t_meas,ncol = 3,nrow = 2))
colnames(t_meas)<-t_colname

t_meas<-tbl_df(t_meas)
t_meas<-t_meas %>% mutate(S_10000=as.character(S_10000),S_20000=as.character(S_20000),S_30000=as.character(S_30000))
t_meas<-t_meas %>% separate(S_10000, into = c('first_10000','Second_10000',"Thrid_10000"), sep=",", extra = 'drop', remove = T) %>% separate(S_20000, into = c('first_20000','Second_20000',"Thrid_20000"), sep=",", extra = 'drop', remove = T) %>% separate(S_30000, into = c('first_30000','Second_30000',"Thrid_30000"), sep=",", extra = 'drop', remove = T)
t_meas<-data.frame(t_meas)
rownames(t_meas)<-t_rowname
#show and summary
t_meas
str(t_meas)
summary(t_meas)
```




## P5
```{r include=F}
# Path to data(I change the path as the given one is not working for some reason)
.datapath <- file.path('C:\\Users\\lianjiayi\\Desktop',
                      'plant-data.txt')
# Read in data
plants <- read.csv(.datapath, strip.white=TRUE, na.strings="")
# Remove annoying columns
.cols2rm <- c('Accepted.Symbol', 'Synonym.Symbol')
plants <- plants[, !(names(plants) %in% .cols2rm)]
# Make names pretty
names(plants) <- c('Scientific_Name', 'Duration', 'Active_Growth_Period',
                   'Foliage_Color', 'pH_Min', 'pH_Max',
                   'Precip_Min', 'Precip_Max',
                   'Shade_Tolerance', 'Temp_Min_F')
```

```{r}
#Relationship between PH and Foliage_Color
#munge
#since there are a huge amount of missing values in pH_Min, pH_Max, and Foliage_Color and fill these NA with a value are going to change their relationship report subjectively, we omit obs having at least one missing value.
#After testing, Foliage_Color has 4334 NAs, pH_Max and pH_Max each has 4327 NAs, and these NAs almost appear at the same obs. Thus, we just use the index indicating where is not NA in Foliage_color to make sure no NA remains in our dat.
plants_adj<-data.frame(Foliage_Color=plants$Foliage_Color[!is.na(plants$Foliage_Color)],pH_Min=plants$pH_Min[!is.na(plants$Foliage_Color)],pH_Max=plants$pH_Max[!is.na(plants$Foliage_Color)])

#Creat new Ph var by average of PH-min and PH-max
plants_adj<-tbl_df(plants_adj)
plants_adj<-plants_adj %>% mutate(Ave_ph=(pH_Min+pH_Max)/2) %>% mutate(norm_ave=Ave_ph-mean(Ave_ph))

# Set number for each color in an order
plants_adj<-plants_adj %>%mutate(Foliage_Color=ifelse(Foliage_Color=='Dark Green',1,Foliage_Color),
Foliage_Color=ifelse(Foliage_Color=='Gray-Green',2,Foliage_Color),
Foliage_Color=ifelse(Foliage_Color=='Green',3,Foliage_Color),
Foliage_Color=ifelse(Foliage_Color=='Red',4,Foliage_Color),
Foliage_Color=ifelse(Foliage_Color=='White-Gray',5,Foliage_Color),
Foliage_Color=ifelse(Foliage_Color=='Yellow-Green',6,Foliage_Color))

#Build Reg model
reg_Plant<-lm(Foliage_Color~norm_ave,plants_adj)

#Coefficients
reg_Plant

#Anova report
anova(reg_Plant)
```