---
title: "HW4_Lian_Jiayi"
author: "Jiayi Lian"
date: "September 20, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
install.packages("lintr", , repo = "https://cran.cnr.Berkeley.edu/")
library('dplyr')
library('tidyr')
library(ggplot2)
library(lintr)
```

## P4
 
Use pip lines to make your code easily understanded. Use explicit returns. Naming vars by connected words. Naming private functions by starting with a dot. File names should end in '.R'. Place spaces around all infix operaters. Limit the number of words in one line.


## P5

```{r}
lint(filename = "C:/Users/lianjiayi/Documents/STAT_5014_2019_-906275604-/HW3_Lian_Jiayi.Rmd")
```
put spaces around all infix operators
only yse double qy=uotes
commas should always have a space after
lines should not be more than 80 characters

## P6

```{r}
device <- readRDS(file = "C:/Users/lianjiayi/Downloads/HW4_data.rds")
device %>% group_by(Observer) %>% mutate(dev1_mean = mean(dev1))

# function plot single boxplot and violin plot
stat_device<-function(rd)
{ 
  level <- as.numeric(levels(factor(rd$Observer)))
  observer = rep(0,length(level))
  mean_dev1 = rep(0,length(level))
  mean_dev2 = rep(0,length(level))
  sd_dev1 = rep(0,length(level))
  sd_dev2 = rep(0,length(level))
  cor_dev = rep(0,length(level))
  for (i in 1:length(level)) {
    observer[i] = level[i]
    mean_dev1[i] = mean(rd$dev1[rd$Observer == level[i]])
    mean_dev2[i] = mean(rd$dev2[rd$Observer == level[i]])
    sd_dev1[i] = sd(rd$dev1[rd$Observer == level[i]])
    sd_dev2[i] = sd(rd$dev2[rd$Observer == level[i]])
    cor_dev[i] = cor(rd$dev2[rd$Observer == level[i]], rd$dev1[rd$Observer == level[i]])
  }
  stat <- data.frame(observer=as.factor(level), mean_dev1=mean_dev1, mean_dev2=mean_dev2, sd_dev1=sd_dev1, sd_dev2=sd_dev2, cor_dev = cor_dev)
    boxplot(stat$mean_dev1,stat$mean_dev2, names = c('dev1',"dev2"), main='compare means of dev1 and dev2')
    p <- stat %>% ggplot() + geom_violin(aes(x="dev1", y=sd_dev1),fill= 'red') + geom_violin(aes(x="dev2", y=sd_dev2),fill = 'blue')+ ylab('value') +ggtitle('Compare sd of dev1 and dev2')
    print(p)
  stat
}
stat_device(device) 

# produce two boxplots and two violin plots

stat_device<-function(rd)
{ 
  level <- as.numeric(levels(factor(rd$Observer)))
  observer = rep(0,length(level))
  mean_dev1 = rep(0,length(level))
  mean_dev2 = rep(0,length(level))
  sd_dev1 = rep(0,length(level))
  sd_dev2 = rep(0,length(level))
  cor_dev = rep(0,length(level))
  for (i in 1:length(level)) {
    observer[i] = level[i]
    mean_dev1[i] = mean(rd$dev1[rd$Observer == level[i]])
    mean_dev2[i] = mean(rd$dev2[rd$Observer == level[i]])
    sd_dev1[i] = sd(rd$dev1[rd$Observer == level[i]])
    sd_dev2[i] = sd(rd$dev2[rd$Observer == level[i]])
    cor_dev[i] = cor(rd$dev2[rd$Observer == level[i]], rd$dev1[rd$Observer == level[i]])
  }
  stat <- data.frame(observer=as.factor(level), mean_dev1=mean_dev1, mean_dev2=mean_dev2, sd_dev1=sd_dev1, sd_dev2=sd_dev2, cor_dev = cor_dev)
    boxplot(stat$mean_dev1, names = c('dev1'),  main='means of dev1')
    boxplot(stat$mean_dev1, names = c('dev2'),  main='means of dev2')
    p1 <- stat %>% ggplot() + geom_violin(aes(x="dev1", y=sd_dev1),fill= 'red') + ylab('value') +ggtitle('sd of dev1')
    print(p1)
    p2 <- stat %>% ggplot() + geom_violin(aes(x="dev2", y=sd_dev2),fill = 'blue')+ ylab('value') +ggtitle('sd of dev2')
    print(p2)
  return(stat)
}
stat_device(device) 

```


```{r}
R_integral<-function(h)
{
  point<- seq(0,1,h)
  integral<- sum(exp(-point^2/2)*h)
  return(integral)
}

width=c(0.1,0.01,0.001,0.0001,0.00001,0.000001)
for (i in 1:length(width)) {
  cat('Width= ',width[i],' Integration= ',R_integral(width[i]),'\n')
}

# Analytic solution is what showed below, but it seems way different from computation result.
sqrt(pi/2*(1-exp(-0.5)))
```      

## P8

```{r}
target_fun<-function(x)
  {
  return(3^x-sin(x)-cos(5*x))
}
dif<-function(x)
{
  return(log(3)*3^x-cos(x)+5*sin(5*x))
}
newton<-function(interval, x)
{
  x0 = x
  path=c(x0)
  y=target_fun(x0)
  while (abs(y)>1e-16) {
    if(x0<interval[1]||x0>interval[2])
    {
      print("Out of the interval")
      break
    }
    x_new=x0-y/dif(x0)
    y=target_fun(x_new)
    x0=x_new
    path=c(path,x_new)
  }
  plot(path,main = "Iteration Path")
  return(path)
}
newton(c(-3,3),0.4)
```

```{r}
b=1
sprintf('c= %s',b)
cat('c',b)

```