---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---


## P2

```{r}
set.seed(12345)
y <- seq(from=1, to=100, length.out = 1e8) + rnorm(1e8)
S=0
ybar=mean(y)

system.time(for (i in 1:length(y)) {
  S=S+(y[i]-ybar)^2
})

system.time(sum((y-ybar)^2))
```

## P3
```{r}
set.seed(1256)
theta <- as.matrix(c(1,2),nrow=2)
X <- cbind(1,rep(1:10,10))
h <- X%*%theta+rnorm(100,0,0.2)
lmfit<-lm(h~0+X)
summary(lmfit)

m=100 
alpha=0.05
theta0=1
theta1=2
theta0_old=0
theta1_old=0
x=rep(1:10,10)
while (abs(theta0-theta0_old)>1e-6 & abs(theta1-theta1_old)>1e-6) {
  theta0_old=theta0
  theta1_old=theta1
  theta0=theta0-alpha*sum(theta0+theta1*x-h)/m
  theta1=theta1-alpha*sum((theta0+theta1*x-h)*x)/m
}

theta0
theta1

```

## P4
```{r}
beta_est<-solve( t(X)%*%X) %*% t(X) %*% h
beta_est
```

This estimator is same as the result from lm(h~0+X)

## P5
```{r}
set.seed(12456) 
G <- matrix(sample(c(0,0.5,1),size=16000,replace=T),ncol=10)
R <- cor(G) # R: 10 * 10 correlation matrix of G
C <- kronecker(R, diag(1600)) # C is a 16000 * 16000 block diagonal matrix
id <- sample(1:16000,size=932,replace=F)
q <- sample(c(0,0.5,1),size=15068,replace=T) # vector of length 15068
A <- C[id, -id] # matrix of dimension 932 * 15068
B <- C[-id, -id] # matrix of dimension 15068 * 15068
p <- runif(932,0,1)
r <- runif(15068,0,1)
C<-NULL #save some memory space
# a
object.size(A)
object.size(B)

system.time({y=p+A%*%solve(B)%*%(q-r)})
```

b) I would calculate matrix addition firstly. Secondly, calculate the inverse of B. Then I product A and inverse of B. Next, AB^-1*(q-r). Finally, p-AB^-1*(q-r).

c)Replace Rblas.dll:
Here are the steps to replace the Rblas.dll file (for Windows users):

1. Check what kind of processor (CPU) your PC or laptop is using (My computer –> Property). Download Rblas.dll from the corresponding directory under http://cran.r-project.org/bin/windows/contrib/ATLAS/.

2. Go to your R directory tp locate where the Rblas.dll is, for example, c:/program files/R/R.2-7.0/bin. Rename it as Rblasold.dll so that if the new Rblass.dll doesn’t fit, you can use the old one by renaming it back.

3. Copy the new Rblass.dll you just download in this folder.

4. Restart R!

reference:https://statmodeling.stat.columbia.edu/2008/06/22/a_trick_to_spee/